---
title: "COVID-19 Projections for Connecticut"
author: 
  - "Forrest W. Crawford, Olga Morozova, Zehang Richard Li, and Soheil Eshghi"
  - "Yale School of Public Health"
  - "Prepared for the Governor's Reopen Connecticut Advisory Group"
date: "`r format(Sys.time(), '%I:%M %p %B %d %Y')`"
header-includes:
  - \usepackage{helvet}
  - \usepackage[T1]{fontenc}
  - \renewcommand\familydefault{\sfdefault} 
output:
  pdf_document:
    toc: true
    fig_crop: false
    fig_width: 7.0
    fig_height: 3.0
fontsize: 11pt
geometry: margin=0.75in
---

```{r, echo=FALSE, include=FALSE}
source("../functions/run_ct_model.R")
mydaymax              = ymd("2020-09-01") 
myschools_reopen_date = ymd("3000-01-01")
mytesting_on_date     = ymd("2020-05-15")

nsim <- 10

# Scenario 1
mylockdown_end_date1   = ymd("2020-06-01") 
mydistancing_stepdown_dates1 = seq(ymd("2020-06-15"), mydaymax, length.out=10)
res1 = get_sir_results(daymax=mydaymax,
                      lockdown_end_date=mylockdown_end_date1,
                      schools_reopen_date=myschools_reopen_date,
                      testing_on_date=mytesting_on_date,
                      distancing_on_date=mylockdown_end_date1+1,
                      distancing_stepdown_dates=mydistancing_stepdown_dates1,
                      nsim=nsim,
                      seed=12345)

# Scenario 2
mylockdown_end_date2   = ymd("2020-07-01") 
mydistancing_stepdown_dates2 = seq(ymd("2020-07-15"), mydaymax, length.out=10)
res2 = get_sir_results(daymax=mydaymax,
                      lockdown_end_date=mylockdown_end_date2,
                      schools_reopen_date=myschools_reopen_date,
                      testing_on_date=mytesting_on_date,
                      distancing_on_date=mylockdown_end_date2+1,
                      distancing_stepdown_dates=mydistancing_stepdown_dates2,
                      nsim=nsim,
                      seed=12345)

# Put into one list
mytitles <- list("Stay-at-home order in place until 6/1", 
               "Stay-at-home order in place until 7/1")
mytitles_long <- list("When the stay-at-home order is in place until June 01", 
                    "When the stay-at-home order is in place until July 01")
res <- list(raw_results = list(res1$raw_results, res2$raw_results), 
            summary = list(res1$summary, res2$summary), 
            titles = mytitles,
            descriptions = mytitles_long)


```


# Introduction 

This report presents projections of COVID-19 hospitalizations and deaths in Connecticut as a whole, and by county. Projections are shown as lines with uncertainty intervals in lighter colors, and actual data (if available) overlaid. Horizontal axes extend to the time horizon for this analysis, `r format(mydaymax, "%B %d, %Y")`.  The report was prepared for the Governor's Reopen Connecticut Advisory group. 

An intervention scenario is described below. Projections under this scenario take into account historical and hypothetical future state-level interventions, including closing of schools on `r format(state_schools_close,"%B %d, %Y")` and the state-level stay-at-home order issued on `r format(state_lockdown_order, "%B %d, %Y")` which took effect on `r format(state_lockdown_start,"%B %d, %Y")`.  School closure is assumed to reduce transmission by `r myparams$school_closure_effect * 100`%, and the state-level stay-at-home order reduces transmission by `r myparams$lockdown_effect * 100`%.  

```{r echo=FALSE, fig.height = 7}
plot_interventions(res$raw_results, mydaymax, stayhome_compare=TRUE, titles=res$titles)
```
The projections presented below evaluate the effect of a hypothetical lifting of the stay-at-home order on **`r format(mylockdown_end_date1, "%B %d, %Y")`** and **`r format(mylockdown_end_date2, "%B %d, %Y")`**. Re-opening of schools is set to be on `r format(myschools_reopen_date, "%B %d, %Y")`.  When the stay-at-home order is lifted, the projections assume an ongoing `r myparams$distancing_effect * 100`% reduction in transmission. 




# Projections 

We first show the projected cumulative deaths and hospitalizations for Connecticut counties over time under the two scenarios. 


```{r echo=FALSE, fig.width=9,  fig.height=3.5}
g <- mapplot_ct_region_list(data = res$summary, which.plot="rD", label="Cumulative\nDeaths", palette="Reds", ncol=3, subtitle=res$titles)
g[[1]]
g[[2]]
```

```{r echo=FALSE, fig.width=9,  fig.height=3.5}
g <- mapplot_ct_region_list(data = res$summary, which.plot="cum_modH",  label="Cumulative\nHospitalizations", palette="Blues", ncol=3, subtitle=res$titles)  
g[[1]]
g[[2]]
```


Projections of deaths and hospitalization for the state and each county are shown below, along with 90% prediction uncertainly intervals.  Hospitalization projections show historical and projected hospital capacity.  

At the county level, hospitalization projections are based on the place of residence, while actual hospitalization data is based on hospital location, not patient residence. 


\clearpage

## Connecticut State 

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
connecticut_summary_deaths = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Connecticut", which.plot="rD")
out = connecticut_summary_deaths
```

`r connecticut_summary_deaths[[1]]`
`r connecticut_summary_deaths[[2]]`



```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
connecticut_summary_hospitalizations = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Connecticut", which.plot="rHsum")
```

`r connecticut_summary_hospitalizations[[1]]`
`r connecticut_summary_hospitalizations[[2]]`




## Fairfield 

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
fairfield_summary_deaths = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Fairfield", which.plot="rD")
```

`r fairfield_summary_deaths[[1]]`
`r fairfield_summary_deaths[[2]]`

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
fairfield_summary_hospitalizations = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Fairfield", which.plot="rHsum")
```

`r fairfield_summary_hospitalizations[[1]]`
`r fairfield_summary_hospitalizations[[2]]`





## New London

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
new_london_summary_deaths = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="New London", which.plot="rD")
```
`r new_london_summary_deaths[[1]]`
`r new_london_summary_deaths[[2]]`

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
new_london_summary_hospitalizations = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="New London", which.plot="rHsum")
```

`r new_london_summary_hospitalizations[[1]]`
`r new_london_summary_hospitalizations[[2]]`






## Litchfield
```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
litchfield_summary_deaths = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Litchfield", which.plot="rD")
```
`r litchfield_summary_deaths[[1]]`
`r litchfield_summary_deaths[[2]]`

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
litchfield_summary_hospitalizations = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Litchfield", which.plot="rHsum")
```

`r litchfield_summary_hospitalizations[[1]]`
`r litchfield_summary_hospitalizations[[2]]`




## Windham
```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
windham_summary_deaths = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Windham", which.plot="rD")
```
`r windham_summary_deaths[[1]]`
`r windham_summary_deaths[[2]]`

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
windham_summary_hospitalizations = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Windham", which.plot="rHsum")
```

`r windham_summary_hospitalizations[[1]]`
`r windham_summary_hospitalizations[[2]]`






## Tolland
```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
tolland_summary_deaths = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Tolland", which.plot="rD")
```
`r tolland_summary_deaths[[1]]`
`r tolland_summary_deaths[[1]]`


```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
tolland_summary_hospitalizations = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Tolland", which.plot="rHsum")
```
`r tolland_summary_hospitalizations[[1]]`
`r tolland_summary_hospitalizations[[2]]`





## Hartford
```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
hartford_summary_deaths = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Hartford", which.plot="rD")
```
`r hartford_summary_deaths[[1]]`
`r hartford_summary_deaths[[2]]`

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
hartford_summary_hospitalizations = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Hartford", which.plot="rHsum")
```

`r hartford_summary_hospitalizations[[1]]`
`r hartford_summary_hospitalizations[[2]]`



## Middlesex
```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
middlesex_summary_deaths = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Middlesex", which.plot="rD")
```
`r middlesex_summary_deaths[[1]]`
`r middlesex_summary_deaths[[1]]`

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
middlesex_summary_hospitalizations = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="Middlesex", which.plot="rHsum")
```

`r middlesex_summary_hospitalizations[[1]]`
`r middlesex_summary_hospitalizations[[2]]`




## New Haven

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
new_haven_summary_deaths = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="New Haven", which.plot="rD")
```
`r new_haven_summary_deaths[[1]]`
`r new_haven_summary_deaths[[2]]`

```{r echo=FALSE, fig.width=10, fig.height=5}
par(mfrow=c(1,2))
new_haven_summary_hospitalizations = plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles, description=res$descriptions, region_name="New Haven", which.plot="rHsum")
```

`r new_haven_summary_hospitalizations[[1]]`
`r new_haven_summary_hospitalizations[[2]]`


# Version

Code version reference: `r system("git rev-parse HEAD", intern=TRUE)`






