---
title: "COVID-19 Projections for Connecticut: Unit tests"
date: "`r format(Sys.time(), '%I:%M %p %B %d %Y')`"
header-includes:
  - \usepackage{helvet}
  - \usepackage[T1]{fontenc}
  - \renewcommand\familydefault{\sfdefault} 
output:
  pdf_document:
    toc: false
    fig_crop: false
    fig_width: 7.0
    fig_height: 3.0
fontsize: 11pt
geometry: margin=0.75in
---

See this document for codes and outputs. Also used as unit test when we make updates. 


### Load data and functions

```{r, echo=TRUE, include=TRUE, message=FALSE,warnings=FALSE}
source("../functions/global_var.R")
mystate0 = get_state0("../data/ct_init.csv")
myparams = yaml.load_file("../parameters/params.yml")  
myposterior = read.csv("../data/posterior_a036.csv", stringsAsFactors=FALSE) 

mydaymax              = ymd("2020-09-01") 
myschools_reopen_date = ymd("3000-01-01")
mytesting_on_date     = ymd("2020-05-15")
mylockdown_end_date   = ymd("2020-06-01") 
mydistancing_stepdown_dates = seq(ymd("2020-06-15"), mydaymax, length.out=10)
nsim = 10
myseed = 12345
```

### Run the projection function

```{r, echo=TRUE, include=TRUE}
res1 = get_sir_results(daymax=mydaymax,
                      lockdown_end_date=mylockdown_end_date,
                      schools_reopen_date=myschools_reopen_date,
                      testing_on_date=mytesting_on_date,
                      distancing_on_date=mylockdown_end_date+1,
                      distancing_stepdown_dates=mydistancing_stepdown_dates,
                      params=myparams,
                      state0=mystate0,
                      nsim=nsim,
                      seed=myseed,
                      posterior = myposterior,
                      draw_rparams = FALSE )
```

### Plot trajectory
```{r, echo=TRUE, include=TRUE}
out1 <- plot_ct_region(res1$summary, end_day=mydaymax, region_name="Connecticut", 
					  which.plot="rD")
out2 <- plot_ct_region(res1$summary, end_day=mydaymax, region_name="Connecticut", 
					  which.plot="rHsum")
```

`r out1`
`r out2`


### Plot trajectory with a shorter time range
```{r, echo=TRUE, include=TRUE}
out <- plot_ct_region(res1$summary, end_day=ymd("2020-06-01"), region_name="New Haven",
					  which.plot="rD", sentence=FALSE)
```

### Plot goodness of fit
```{r, echo=TRUE, include=TRUE, fig.width=10}
par(mfrow = c(1, 2))
out <-    plot_ct_region(data=res1$summary, region_name="Connecticut", which.plot="rD",
                title.override="Cumulative deaths", goodness=TRUE)
out <-    plot_ct_region(data=res1$summary, region_name="Connecticut", which.plot="rHsum",
                title.override="Required hospitalization", goodness=TRUE)

```


### Plot new trajectories
```{r, echo=TRUE, include=TRUE}
out <- plot_ct_region(res1$summary, end_day=mydaymax, region_name="New Haven",
            which.plot="NH", sentence=FALSE)
```

```{r, echo=TRUE, include=TRUE}
out <- plot_ct_region(res1$summary, end_day=mydaymax, region_name="Connecticut",
            which.plot="currentI_prop", sentence=FALSE)
```


### Plot maps
```{r, echo=TRUE, include=TRUE}
mapplot_ct_region(data = res1$summary, which.plot="rD", label="Cumulative\nDeaths",
			      palette="Reds", ncol=3, subtitle=NULL)
```

\clearpage
# Plot trajectories in two scenarios

### Fit another scenario

```{r, echo=TRUE, include=TRUE}
mylockdown_end_date2   = ymd("2020-07-01") 
mydistancing_stepdown_dates2 = seq(ymd("2020-07-15"), mydaymax, length.out=10)
res2 = get_sir_results(daymax=mydaymax,
                      lockdown_end_date=mylockdown_end_date2,
                      schools_reopen_date=myschools_reopen_date,
                      testing_on_date=mytesting_on_date,
                      distancing_on_date=mylockdown_end_date2+1,
                      distancing_stepdown_dates=mydistancing_stepdown_dates2,
                      params=myparams,
                      state0=mystate0,
                      nsim=nsim,
                      seed=myseed,
                      posterior = myposterior,
                      draw_rparams = FALSE )
```

### Organize results into a list

As this gets more complicated, this is where we do additional processing, e.g., taking differences.

```{r, echo=TRUE, include=TRUE}
# Put into one list
mytitles <- list("Stay-at-home order in place until 6/1", 
               "Stay-at-home order in place until 7/1")
mytitles_long <- list("When the stay-at-home order is in place until June 01", 
                    "When the stay-at-home order is in place until July 01")
res <- list(raw_results = list(res1$raw_results, res2$raw_results), 
            summary = list(res1$summary, res2$summary), 
            titles = mytitles,
            descriptions = mytitles_long)
```

### Plot trajectories with the same Y axis
```{r, echo=TRUE, include=TRUE, fig.width=10, fig.height=4}
out <- plot_ct_region_list(data=res$summary, end_day=mydaymax, title=res$titles,
						   description=res$descriptions, 
						   region_name="Connecticut", which.plot="rD")
```
`r out[[1]]`
`r out[[2]]`

### Plot maps with the same Y axis
```{r, echo=TRUE, include=TRUE, fig.width=10, fig.height=4}
g <- mapplot_ct_region_list(data = res$summary, which.plot="cum_modH",  label="Cumulative\nHospitalizations", palette="Blues", ncol=3, subtitle=res$titles)
g[[1]]
g[[2]]
```


### Version 
Code version reference: `r system("git rev-parse HEAD", intern=TRUE)`






