---
title: "COVID-19 Projections for Connecticut: Key Parameters"
date: "`r format(Sys.time(), '%I:%M %p %B %d %Y')`"
header-includes:
  - \usepackage{helvet}
  - \usepackage[T1]{fontenc}
  - \renewcommand\familydefault{\sfdefault} 
output:
  pdf_document:
    toc: false
    fig_crop: false
    fig_width: 7.0
    fig_height: 3.0
fontsize: 11pt
geometry: margin=0.75in
---

```{r, echo=FALSE, include=FALSE}
#source("run_ct_model.R")
library(yaml)
params_init = yaml.load_file("params.yml") 
```


# Key epidemiologic parameters 

## Case type distribution

Probability of severe disease that requires hospitalization and may lead to death: `r 1 - params_init$q_Im - params_init$q_A`. 

Probability of mild disease that does not require hospitalization and will lead to recovery: `r params_init$q_Im`. 

Probability of asymptomatic infection: `r params_init$q_A`. 

## Probability of death

Probability of death given hospitalization: `r params_init$m_H`

## Reproductive numbers

```{r, echo=FALSE, include=FALSE}
R0 = params_init$beta_pre * (params_init$q_A * params_init$k_A * (1/params_init$gamma_A) + params_init$q_Im * (1/params_init$gamma_Im) + (1- params_init$q_Im - params_init$q_A) * (1/params_init$alpha))
```
Basic reproductive number: `r round(R0, 1)`.

Reproductive number after school closure: `r round(R0 * (1 - params_init$school_closure_effect), 1)`

Reproductive number after school closure and lockdown: `r round(R0 * (1 - params_init$school_closure_effect) * (1 - params_init$lockdown_effect), 1)`

### Version: 
Code version reference: `r system("git rev-parse HEAD", intern=TRUE)`






