---
title: "COVID-19 Projections for Connecticut"
author: 
  - "Forrest W. Crawford, Olga Morozova, Zehang Richard Li, and Soheil Eshghi"
  - "Yale School of Public Health"
  - "Prepared for the Governor's Reopen Connecticut Advisory Group"
date: "`r format(Sys.time(), '%I:%M %p %B %d %Y')`"
header-includes:
  - \usepackage{helvet}
  - \usepackage[T1]{fontenc}
  - \renewcommand\familydefault{\sfdefault} 
output:
  pdf_document:
    toc: true
    fig_crop: false
    fig_width: 7.0
fontsize: 11pt
geometry: margin=0.75in
---

```{r, echo=FALSE, include=FALSE}
source("run_ct_model.R")

```


# Introduction 

This report presents projections of COVID-19 hospitalizations and deaths in Connecticut as a whole, and by county.  The report was prepared for the Governor's Reopen Connecticut Advisory group. 


## Data sources

Hospital capacity and occupancy

map data

Historical and actual interventions

## Model assumptions


The projections in this document were created using a customized SEIR infectious disease transmission model, augmented with asymptomatic, moderate, and severe infection categories, hospitalization, and death.  The model includes time-varying hospital capacities for each county; when occupancy reaches capacity, unhospitalized patients with severe disease are assumed to be `r params_init$m_Hbar_mult` times more likely to die.  

The model incorporates features of the public health information and recordkeeping during covid-19 outbreak, including a case reporting lag of `r params_init$rcase_lag` days, hospital reporting lag of `r params_init$rhosp_lag` days, and a death reporting lag of `r params_init$rdeath_lag` days. 

The model also accommodates past and potential future interventions, including stay-at-home orders, school and business closures, and social distancing measures targeting specific demographic groups.   

[Describe these features and parameters]

percent reduction in contact due to stay-at-home order is `r params_init$effect_intvx`


# Projections 

We present projections of COVID-19 deaths and hospitalizations for Connecticut as a whole, followed by projections by county.  Projections are shown as lines with uncertainty intervals in lighter colors, and actual data (if available) overlaid. Horizontal axes extend to the time horizon for this analysis, `r format(daymax, "%b %d, %Y")`. 




## Connecticut State 

The projections take into account historical and hypothetical future state-level interventions, including closing of schools on `r format(state_schools_close,"%b %d, %Y")` and the state-level stay-at-home order issued on `r format(state_lockdown_start,"%b %d, %Y")` which took effect on `r format(state_lockdown_order, "%b %d, %Y")`.  

School closure is assumed to reduce transmission by `r params_init$school_closure_effect * 100`%, and the state-level stay-at-home order reduces transmission by `r params_init$lockdown_effect * 100`%.  

These projections evaluate the effect of a hypothetical lifting of the stay-at-home order on `r format(lockdown_end_date, "%b %d, %Y")` and re-opening of schhols on `r format(state_schools_reopen_date, "%b %d, %Y")`. 

When the stay-at-home order is lifted, the projections assume an ongoing `r params_init$distancing_effect * 100`% reduction in transmission. 


```{r echo=FALSE}
plot_interventions()
```


```{r echo=FALSE}
connecticut_summary = plot_ct_region("Connecticut")
mapplot_ct_region()
```


`r connecticut_summary`





## Fairfield 

```{r echo=FALSE}
fairfield_summary = plot_ct_region("Fairfield")
```

`r fairfield_summary`



## New London

```{r echo=FALSE}
new_london_summary = plot_ct_region("New London")
```
`r new_london_summary`


## Litchfield
```{r echo=FALSE}
plot_ct_region("Litchfield")
```
`r connecticut_summary`



## Windham
```{r echo=FALSE}
windham_summary = plot_ct_region("Windham")
```
`r windham_summary`



## Tolland
```{r echo=FALSE}
tolland_summary = plot_ct_region("Tolland")
```
`r tolland_summary`



## Hartford
```{r echo=FALSE}
hartford_summary = plot_ct_region("Hartford")
```
`r connecticut_summary`



## Middlesex
```{r echo=FALSE}
middlesex_summary = plot_ct_region("Middlesex")
```
`r middlesex_summary`



## New Haven

```{r echo=FALSE}
new_haven_summary = plot_ct_region("New Haven")
```
`r new_haven_summary`



# About this document

This document is generated from [Rmarkdown](https://rmarkdown.rstudio.com/) using code in the Github repository <https://github.com/fcrawford/covid19_ct>. 

## Authors

Forrest W. Crawford is an Associate Professor of Biostatistics, Statistics & Data Science, Operations, and Ecology & Evolutionary Biology at Yale University. He is affiliated with the Center for Interdisciplinary Research on AIDS, the Institute for Network Science, the Computational Biology and Bioinformatics Program, and the Public Health Modeling Unit.  

Olga Morozova, Zehang Richard Li, and Soheil Eshghi are Postdoctoral Associates in the Department of Biostatistics at the Yale School of Public Health. 

<http://www.crawfordlab.io>

<http://campuspress.yale.edu/omorozova/>

<https://zehangli.com/>

<http://www.soheileshghi.com/>

## Citation

To cite this document: 

> Forrest W. Crawford, Olga Morozova, Zehang Richard Li, Soheil Eshghi.  COVID-19 Projections for Connecticut.  `r format(Sys.time(), '%B %d %Y')`. 

Code version reference: `r system("git rev-parse HEAD", intern=TRUE)`

```{r echo=FALSE}
system("git status --porcelain", intern=TRUE)
```




