---
title: "COVID-19 Projections for Connecticut"
author: 
  - "Forrest W. Crawford, Olga Morozova, Zehang Richard Li, and Soheil Eshghi"
  - "Yale School of Public Health"
  - "Prepared for the Governor's Reopen Connecticut Advisory Group"
date: "`r format(Sys.time(), '%I:%M %p %B %d %Y')`"
header-includes:
  - \usepackage{helvet}
  - \usepackage[T1]{fontenc}
  - \renewcommand\familydefault{\sfdefault} 
output:
  pdf_document:
    toc: true
    fig_crop: false
fontsize: 11pt
geometry: margin=1in
---

```{r, echo=FALSE, include=FALSE}
source("run_ct_model.R")

```


# Introduction 

This document presents projections of COVID-19 infections, hospitalizations, and deaths in Connecticut counties, and the state as a whole.  

## Data sources

## Model assumptions

To describe parameters, use the yaml info! 

The case reporting lag is `r params_init$rcase_lag` days 

hospital reporting lag is `r params_init$rhosp_lag` days

death reporting lag is `r params_init$rdeath_lag` days 

percent reduction in contact due to stay-at-home order is `r params_init$effect_intvx`


## Hospital capacity and occupancy 


## Historical and actual interventions


## Future intervention scenarios




# Projections 

## Connecticut State 

```{r, echo=FALSE}
connecticut_summary = plot_ct_region("Connecticut")
```
`r connecticut_summary`

## Fairfield 

```{r echo=FALSE}
fairfield_summary = plot_ct_region("Fairfield")
```

`r fairfield_summary`



## New London

```{r echo=FALSE}
new_london_summary = plot_ct_region("New London")
```
`r new_london_summary`


## Litchfield
```{r echo=FALSE}
plot_ct_region("Litchfield")
```
`r connecticut_summary`



## Windham
```{r echo=FALSE}
windham_summary = plot_ct_region("Windham")
```
`r windham_summary`



## Tolland
```{r echo=FALSE}
tolland_summary = plot_ct_region("Tolland")
```
`r tolland_summary`



## Hartford
```{r echo=FALSE}
hartford_summary = plot_ct_region("Hartford")
```
`r connecticut_summary`



## Middlesex
```{r echo=FALSE}
middlesex_summary = plot_ct_region("Middlesex")
```
`r middlesex_summary`



## New Haven

```{r echo=FALSE}
new_haven_summary = plot_ct_region("New Haven")
```
`r new_haven_summary`



# About


## Data Sources 

## Model structure 

## Parameterization 

## About the authors

Forrest W. Crawford is an Associate Professor of Biostatistics, Statistics & Data Science, Operations, and Ecology & Evolutionary Biology at Yale University. He is affiliated with the Center for Interdisciplinary Research on AIDS, the Institute for Network Science, the Computational Biology and Bioinformatics Program, and the Public Health Modeling Unit.

Olga Morozova is... 

Zehang Richard Li is...

Soheil Eshghi...

Lab website: <http://www.crawfordlab.io>

## Citation

To cite this document: 

> Forrest W. Crawford, Olga Morozova, Zehang Richard Li, Soheil Eshghi.  COVID-19 Projections for Connecticut.  `r format(Sys.time(), '%B %d %Y')`. 


## About this document

This document is generated from [Rmarkdown](https://rmarkdown.rstudio.com/) using code in the Github repository <https://github.com/fcrawford/covid19_ct>. 

Code version reference: `r system("git rev-parse HEAD", intern=TRUE)`

`r system("git status --porcelain", intern=TRUE)`

